### 2023-01-18 paper-thesis/chapters/12-editor-services.tex
Minor fix

\section{How well it works}
In order to get suggestions, we can now insert a placeholder \verb|[[Expr]]| and press \verb|ctrl + space| in the editor to get semantic suggestions.

>>>>

\section{Quality of suggestions}
In order to get suggestions, we can now insert a placeholder \verb|[[Expr]]| and press \verb|ctrl + space| in the editor to get semantic suggestions.
